---
title: "Group Data Analysis"
author: "Group hisRüstü"
output: html_document
---

## Preprocessing the Data
In the data, 81 provinces of Turkey contain information about first-hand and second-hand home price indexes. Migration movements in cities, economic movements throughout the country and some changes in cities, such as opening factories, are some of the factors that affect home price index data.
Some packages need to be used to analyze the data. To start with, the packages are downloaded and the data is read from the csv file.

```{r setup, include=FALSE}

library(tidyverse)
library(lubridate)
library(dplyr)
library(cluster)
library(factoextra)
library(sp) 
library(openxlsx)
library(mapproj)
library(gridExtra)
library(ggthemes)
library(tseries)
library(forecast)
library(readxl)
library(data.table)
library(ggplot2)
library(car)

evds = read.csv("https://raw.githubusercontent.com/pjournal/boun01g-hisrustu/gh-pages/housing_data_EVDS.csv")

url <- "https://raw.githubusercontent.com/pjournal/boun01g-hisrustu/gh-pages/TUR_1_sp.rds"

TUR <- readRDS(url(url, method="libcurl"))

TUR_fixed <- fortify(TUR)

```

**There are Turkish characters in the eds data. "convertName" function converts them to the English characters. However due to Excel version differences some computers use different special characters. So if our code gives an error in a different computer, it is probably due to this part.**
```{r echo=TRUE}
convertName<-function(data,handLabel){
  data <- gsub(".*- (.+) -.*", "\\1", data)
  data <- gsub("\u008d", "i", data)
  data <- gsub("€", "C", data)
  data <- gsub("ž", "S", data)
  data <- gsub("Ÿ", "s", data)
  data <- gsub("\u0081", "u", data)
  data <- gsub("˜", "I", data)
  data <- gsub("§", "g", data)
  data <- gsub("”", "o", data)
  data <- paste(handLabel, data, sep="_")
  return(data)
}
```

After the 92nd row, rows give information about the numericalvalues.Therefore, numerical data was separated from the rows that contain information were put into another data set.

```{r echo=FALSE}

datainfo = evds[c(92:1080),]
cityNames<-evds[c(95:258),2]
firstHandCityNames<-cityNames[c(1:82)]
secondHandCityNames<-cityNames[c(83:164)]
evds = evds[c(1:91),]
firstHandCityNames<-convertName(firstHandCityNames,"F")
secondHandCityNames<-convertName(secondHandCityNames,"S")
allNames= c("Tarih",firstHandCityNames,secondHandCityNames)
names(evds)<-allNames
```

The house price index data included data with zeros after the comma. To avoid these problems, zeros are cleared from the data after the comma.

```{r pressure, echo=TRUE}
for(i in c(1:165)){
  evds[,i] <- gsub(",","",evds[,i])
}
evds[, c(2:165)] <- sapply(evds[, c(2:165)], as.numeric)
names(evds)[1] = "Date"
```

In order to convert the Date column to a date format, it was necessary to add days to the Date. That's why the day was added to the Date column.

```{r echo=TRUE}
evds$Date = paste(evds$Date,"01",sep="-")
evds = evds %>%
  mutate(Date=as.Date(Date, format="%Y-%m-%d")) %>%
  mutate(Year=year(Date), Month=month(Date))

```

In the data analysis process, a season column may be required to examine the relationship between price index data and seasons, so the season column was created.

```{r}
find_season <- function(mon){
  season = NULL
  
  if(between(mon, 3, 5)){
    season = "Spring"
  } else if(between(mon, 6, 8)){
    season = "Summer"
  } else if(between(mon, 9, 11)){
    season = "Fall"
  } else{
    season = "Winter"
  }
  
  return(season)
}
evds$Season = sapply(evds$Month, find_season)
```


When the data is checked carefully, there is some missing data. To guess what these missing data are:
Total data was analyzed by collecting all data.
As it is realized that it is equal, empty data (NA) are accepted as 0.

```{r echo=TRUE}
evds[,c(2)] - rowSums(evds[,c(3:83)], na.rm = FALSE)
evds[,c(2)] - rowSums(evds[,c(3:83)], na.rm = TRUE)
evds[is.na(evds)] <- 0
```

## Analyzing the Data
A plot line has been drawn to observe the price index movement of the first and second hand houses by years. As can be seen from the graphic, the house price index increased every year.

```{r echo=TRUE}
ggplot(evds, aes(x=Date)) + 
  geom_line(aes(y=S_Turkey, color="S")) + 
  geom_line(aes(y=F_Turkey, color="F")) +
  theme_minimal() + 
  ggtitle("Sum of Pricing Indexes") + 
  labs(x = "Year", y = "Pricing Index")+
  scale_color_manual(name="Price index type", labels=c("Firsthand","Secondhand"),values=c("red","blue"))

```

In Turkey, the behavior of price index in general, the city has been interpreted by comparing the behavior of a relationship between them. As can be seen in the graph, the price index of Adana is similar to the price index data across the country. We cannot generalize for every city, but we can say that the same criteria are effective across the country.

```{r}
ggplot(evds, aes(x=Date, color = Month)) + 
  geom_line(aes(y=S_Adana, color="S1")) + 
  geom_line(aes(y=F_Adana, color="F1")) +
  theme_minimal() + 
  ggtitle("Price Index of Adana Over The Years") + 
  labs(x = "Year", y = "Pricing Index")+
  scale_color_manual(name="Price index type", labels=c("Firsthand","Secondhand"),values=c("red","blue"))

```

In the two largest cities of Turkey, Ankara and Istanbul, the price index data were examined separately. When the data of the two cities are analyzed on the graph, the price index data of Istanbul is higher than Ankara's. When the sum of the data of all cities is plotted, the total price index of Ankara and Istanbul is very high compared to other cities.

```{r}
ggplot(evds, aes(x=Date, color = Month)) + 
  geom_line(aes(y=S_Ankara, color="S_Ankara")) + 
  geom_line(aes(y=F_Ankara, color="F_Ankara")) +
  geom_line(aes(y=S_Istanbul, color="S_Istanbul")) + 
  geom_line(aes(y=F_Istanbul, color="F_Istanbul")) +
  theme_minimal() + 
  ggtitle("Comparison of Price Indexes Between Ankara and Istanbul") + 
  labs(x = "Year", y = "Price Index")+
  scale_color_manual(name="Price index type", labels=c("Firsthand Ankara","Firsthand Istanbul", "Secondhand Ankara","Secondhand Istanbul"),values=c("darkred","darkblue","red","lightblue"))

```

## Plot Analysis

evds2 contains the percentage of the values that make up to the total, abnormal changes can be observed and a result can be concluded:

```{r}
evds2 = evds
evds2[,c(2:83)] = evds2[,c(2:83)]*100/evds2[,2]
evds2[,c(84:165)] = evds2[,c(84:165)]*100/evds2[,84]
```

In order to examine the house price index data of the Aegean Region and Antalya, whose population increases considerably during the summer season, some of the cities in the Aegean Region and Antalya  were selected.


```{r}
ege_bolge <- evds[,c(1,10,14,43,13,61,166,167,168)]
head(ege_bolge)
```


Between 2013 and 2020, a bar plot was drawn for Antalya's price index data grouped by months. By observing the year-by-year price index movement, it can be said that the price index has increased each year, moreover, the price index is increasing every year in summer months.

```{r}

ege_bolge %>%  group_by(Month,Season) %>% summarise(Sum = sum(F_Antalya)) %>%
  ggplot(data = ., aes(x = Month, y = Sum, fill = Season)) +
  geom_bar(stat="identity", position = position_dodge(), colour = "blue") +
  theme_minimal() +
  theme(legend.position="top")+
  labs(title = "Price Index Sum of Antalya Grouped by Months", y="Price Index Sum")+
  geom_text(aes(label=Sum), vjust=1.6, color="black",
      position = position_dodge(0.9), size=3.5)+
  scale_x_continuous(breaks=c(3,6,9,12))

```

Between 2013 and 2020, a line plot was drawn for Balıkesir's price index data grouped by months. By observing the month-by-month price movement, it can be said that the price index has increased at the end of the year.
```{r}
ggplot(ege_bolge, aes(x=Month, y = ege_bolge[,c(2:2)], group = Year, colour = Season)) + 
  geom_line() +
  theme_minimal() +
  theme(legend.position="top")+
  labs(title = "Price Index of Balıkesir Over Months",y="Monthly Price Index")+
  scale_x_continuous(breaks=c(3,6,9,12))

```

Total price index data by years and seasons by selected cities in the Aegean region with bar chart

```{r}
#
ege_bolge %>% group_by(Year,Season) %>% summarise(SumData=sum(F_Antalya, F_Balikesir, F_Izmir, F_Aydin, F_Mugla)) %>% 
    ggplot(data = ., aes(x = Year, y = SumData, fill = Season)) +
      geom_bar(stat="identity", position = position_dodge(), colour = "black") +
      theme_minimal() +
      theme(legend.position="top")+
   labs(title = "Sum of Price Indexes of Aegean Region Grouped By Seasons",y="Price Index Sum")

```

### Clustering by Housing Price Index

In this section, we tried to group cities according to how similar they are to each other and find similarity within a cluster using the k-means algorithm.

Moving on with the clustering, it is desired to analyze the sales behavior more logically by classifying data of the cities according to the similarities of the index movement. Therefore, all columns are scaled.


```{r}
changeClusterName <- function(cl){
  name = NULL
  
  if(cl == 1){
    name = "Cluster A"
  } else if(cl == 2){
    name = "Cluster B"
  } else if(cl == 3){
    name = "Cluster C"
  } else if(cl == 4){
    name = "Cluster D"  
} else if(cl == 5){
    name = "Cluster E"
  }
  return(name)
}

createCluster<-function(data,clusterSize,scale=TRUE){
  
  if(scale){
    data<-scale(data)
  }
  set.seed(2)
  fit <- kmeans(t(data), clusterSize)
  fit$cluster = sapply(fit$cluster, changeClusterName)


  return(fit$cluster)
}


clusters = tibble(TUR@data$NAME_1)
names(clusters)=c("city")
clusterSize=5

clusters<-cbind(clusters,createCluster(evds[,c(3:83)],clusterSize))
clusters<-cbind(clusters,createCluster(evds[,c(3:83)],clusterSize,scale=FALSE))
clusters<-cbind(clusters,createCluster(evds[,c(85:165)],clusterSize))
clusters<-cbind(clusters,createCluster(evds[,c(85:165)],clusterSize,scale=FALSE))
clusters<-cbind(clusters,createCluster(evds[,c(85:165)]-evds[,c(3:83)],clusterSize))
names(clusters)<-c("city","First","nonScaleFirst","Second","nonScaleSecond","firstMinusSecond")
row.names(clusters)<-NULL


```

```{r}
mapPlot<-function(data,columnName,mapPositions){
  
mapPositions2<-cbind(mapPositions,data)

ab<-cbind(c(1:81),mapPositions2)
ab[,1]=as.character(ab[,1])
colnames(ab)[1]="id"

final_map <- left_join(TUR_fixed, ab, by = "id")


ggplot(final_map)+
  theme_minimal()+
  geom_polygon( aes_string(x = "long", y = "lat", group = "group", fill= columnName),
                color = "grey", alpha = 1/5) +
  coord_map()  +labs(title=paste(paste("Cities by",columnName),"Hand Housing Price Index"),fill= "Clusters")+
  theme(legend.position = "bottom") # change the legend position

}

mapPositions = tibble(TUR@data$NAME_1)
names(mapPositions)=c("city")
```


In the First Hand Price Index Plot according to the index movements, Antalya and İzmir are in the same cluster. Probably, the seasonal movements of being a summer vacation city are similar to each other. Adana and Ankara are in the same cluster. This cluster also includes many cities in the Central Anatolia Region. That’s why, there may be a regional effect in this cluster. Interestingly, Istanbul is in the same cluster with Şanlıurfa and Mardin. The probable reason for this may be the recent Syrian migration.
```{r}
mapPlot(clusters[,c(2:5)],"First",mapPositions)
```

In the Second Hand Price Index Plot it is seen that the movements in metropolitan cities are similar. Istanbul, Izmir and Antalya are in the same cluster. Adana and Ankara are in a different cluster. Although other cities look irregular, we see that nearby cities have the same colors. We can say that there is a regional effect, even if it is small.

```{r}
mapPlot(clusters[,c(2:5)],"Second",mapPositions)
```


İstanbul, Ankara, Adana, Kayseri, Antalya, Bursa, Eskişehir, Mersin, and Van are among the largest 30 cities in Turkey. To see the difference between first-hand and second-hand prices, the means of their respective price index are calculated. As a common fact, first-hand prices are higher than the second-hand prices. However, Van shows an exceptional result as its second-hand price is higher. The plot is generated to show how large the difference is among these cities. Ankara and İstanbul are the leading cities in terms of the price gap, with Ankara on top and İstanbul the runner-up.

```{r}
S_means <- c(mean(evds$S_Istanbul),mean(evds$S_Ankara),mean(evds$S_Adana),mean(evds$S_Kayseri),mean(evds$S_Antalya),mean(evds$S_Bursa),mean(evds$S_Eskisehir), mean(evds$S_Mersin),mean(evds$S_Van))
F_means <- c(mean(evds$F_Istanbul),mean(evds$F_Ankara),mean(evds$F_Adana),mean(evds$F_Kayseri),mean(evds$F_Antalya),mean(evds$F_Bursa),mean(evds$F_Eskisehir), mean(evds$F_Mersin),mean(evds$F_Van))
cities<- c("Istanbul","Ankara","Adana","Kayseri","Antalya","Bursa","Eskişehir","Mersin","Van")
large_city_data <- data.frame(cities, S_means, F_means)

ggplot(large_city_data)+
  geom_point(aes(S_means,cities,color="red"))+
  geom_point(aes(F_means,cities,color="green"))+
  geom_segment(aes(x = S_means,y = cities,xend = F_means,yend = cities,),arrow=arrow(length = unit(0.15, "inches")))+
  theme_gdocs()+
  labs(x="First-hand and Second-hand Means", y="Large Cities", title="First-hand and Second-hand Prices of Large Cities")+
  scale_color_manual(name="Index Type",labels=c("Second-hand","First-hand"),values=c("red","green"))+
  theme(
    text= element_text(size=8, color="black")
    
  )
```


## Time Series Analysis

In order to conduct Time Series Analysis, the data should be converted to time series in format. Then we see that variance is increasing over time meaning that it's multiplicative. Also, it may include seasonality. The series can be interpreted  better by decomposition. The decomposed time series is plotted below.

```{r}
ts_F_Turkey <- ts(evds$F_Turkey,freq=12,start = 2013)
ts_F_Turkey

plot(ts_F_Turkey, main = "Time Series Plot", ylab = "F_Turkey")
plot(decompose(ts_F_Turkey, type = "multiplicative"))
```

After the time series visualization and analysis, the auto correlation function of the time series is plotted. The auto correlation values peak at lag 12 and at lag 24, which means that there is a monthly seasonality factor.

```{r}
acf(ts_F_Turkey, lag.max = 24)
```

Observing the time series plot of the data, it’s seen that variance changes over time. Thus, a transformation is needed due to this non-stationarity. After the logarithmic transformation, the change is visible on the graph below.

```{r}
ts_F_Turkey_log <- ts(log(evds$F_Turkey),freq=12,start = 2013)

ts_F_Turkey_log_reg_diff=diff(ts_F_Turkey_log)
tsdisplay(ts_F_Turkey_log_reg_diff, lag.max = 24)
```

After logarithmic transformation, it’s seen that differencing is needed; therefore, one order regular differencing is applied. In the figure below, you can see the significant acf values at different lags. They peak at lags 12, 24 and so on. This pattern means that seasonality and seasonal differencing is needed.

```{r}
ts_F_Turkey_log_reg_s_diff=diff(ts_F_Turkey_log_reg_diff,12)
tsdisplay(ts_F_Turkey_log_reg_s_diff, lag.max = 24)
```

ACF and PACF plots of the time series suggest ARIMA (1,0,0)(2,0,0) 12.

```{r}
model_first <- Arima(ts_F_Turkey_log, order=c(1,0,0), seasonal=c(2,0,0))
model_first
```

The statistical evidence can be found with the inspection of the residuals of the model. The residuals should be normal and the Q-Q plot can be used for inspection.

```{r}
resid <- model_first$residuals
tsdisplay(resid)

qqPlot(resid)

plot(c(model_first$residuals), main="Scatter Plot of Residuals", xlab = "Time
     Index", ylab = "Residuals")
```

The Q-Q plot suggests that the residuals are distributed normally but at the extreme sides there are outliers. We tried to explain all the months but it could not be explained fully. Secondly, the scatter plot is examined, we want the residuals to be random. As can be seen, the residuals are almost random, except, just the left hand side.

## Time Series - Future Prediction (2020-2)

We're good to go with the model. Therefore, we can now predict next months. Let's predict the second half of 2020.

```{r}
forecast_sales=forecast(model_first , h=5)
real_forecast=exp(forecast_sales$mean)
real_forecast
```

Note that to make the multiplicative model additive, we conducted a log
transformation, hence, they are transformed them back to the obtained forecast.
Plot the forecast to see the pattern.

```{r}
plot(forecast(model_first, h=5), main="F_Turkey")
```

Similar procedures are followed and predictions are made for the secondhand sales level("S_Turkey").

```{r, echo=FALSE, message=FALSE}
ts_S_Turkey <- ts(evds$S_Turkey,freq=12,start = 2013)
ts_S_Turkey_log <- ts(log(evds$S_Turkey),freq=12,start = 2013)

ts_S_Turkey_log_reg_diff=diff(ts_S_Turkey_log)
#tsdisplay(ts_S_Turkey_log_reg_diff, lag.max = 24)

ts_S_Turkey_log_reg_s_diff=diff(ts_S_Turkey_log_reg_diff,12)
#tsdisplay(ts_S_Turkey_log_reg_s_diff, lag.max = 24)

model_second <- Arima(ts_S_Turkey_log, order=c(2,1,2), seasonal=c(1,0,0))
model_second

resid <- model_second$residuals
#tsdisplay(resid)

#qqPlot(resid)

#plot(c(model_second$residuals), main="Scatter Plot of Residuals", xlab = "Time
#     Index", ylab = "Residuals")

forecast_sales=forecast(model_second , h=5)
forecast_sales
real_forecast_second=exp(forecast_sales$mean)
```

```{r}
real_forecast_second
plot(forecast(model_second, h=5), main="S_Turkey")
```

Similar procedures followed and predictions made for second hand price index level("F_Antalya") this time.

```{r, echo=FALSE, message=FALSE}
ts_F_Antalya <- ts(evds$F_Antalya,freq=12,start = 2013)
ts_F_Antalya_log <- ts(log(evds$F_Antalya),freq=12,start = 2013)

#ts_S_Turkey_log_reg_diff=diff(ts_S_Turkey_log)
#tsdisplay(ts_S_Turkey_log_reg_diff, lag.max = 24)

#ts_S_Turkey_log_reg_s_diff=diff(ts_S_Turkey_log_reg_diff,12)
#tsdisplay(ts_S_Turkey_log_reg_s_diff, lag.max = 24)

model_first_antalya <- Arima(ts_F_Antalya_log, order=c(0,1,1), seasonal=c(2,0,0))
model_first_antalya

#resid <- model_first_antalya$residuals
#tsdisplay(resid)

#qqPlot(resid)

#plot(c(model_second$residuals), main="Scatter Plot of Residuals", xlab = "Time
#     Index", ylab = "Residuals")

forecast_sales=forecast(model_first_antalya , h=5)
forecast_sales
real_forecast_f_antalya=exp(forecast_sales$mean)
```

```{r}
real_forecast_f_antalya
plot(forecast(model_first_antalya, h=5), main="F_Antalya")
```

## Time Series - Future Prediction (2020 Plots)

PS: Note that to make the multiplicative model additive we made log
transformation, so we will transform them back to obtained forecasts.

### Turkey's First Sales in 2020

```{r}
t_first_2020 <- c(ts_F_Turkey[85:91], real_forecast)
plot_list = list(real_value = data.frame(x=c(1:7), y=t_first_2020[1:7]),
                  forecasted = data.frame(x=c(7:12), y=t_first_2020[7:12]))
ggplot(bind_rows(plot_list, .id="types"), aes(x, y, colour=types)) + geom_line() + ggtitle("Turkey's First Sales in 2020")+ scale_x_continuous(breaks=c(3,6,9,12)) +labs(x="Months", y="Sales")
```

### Turkey's Secondhand Sales in 2020

```{r}
t_second_2020 <- c(ts_S_Turkey[85:91], real_forecast_second)
plot_list = list(real_value = data.frame(x=c(1:7), y=t_second_2020[1:7]),
                  forecasted = data.frame(x=c(7:12), y=t_second_2020[7:12]))
ggplot(bind_rows(plot_list, .id="types"), aes(x, y, colour=types)) + geom_line() + ggtitle("Turkey's Secondhand Sales in 2020")+ scale_x_continuous(breaks=c(3,6,9,12)) +labs(x="Months", y="Sales")
```

### Antalya's First Sales in 2020

```{r}
antalya_2020 <- c(ts_F_Antalya[85:91], real_forecast_f_antalya)
plot_list = list(real_value = data.frame(x=c(1:7), y=antalya_2020[1:7]),
                  forecasted = data.frame(x=c(7:12), y=antalya_2020[7:12]))
ggplot(bind_rows(plot_list, .id="types"), aes(x, y, colour=types)) + geom_line() + ggtitle("Antalya's First Sales in 2020") + scale_x_continuous(breaks=c(3,6,9,12)) +labs(x="Months", y="Sales")
```