---
title: "Group Data Analysis"
author: "Group hisa'R'üstü"
output: html_document
---

>Editing Data

These data, in the 81 provinces of Turkey contains the information first-hand and second-hand home sales. These data, in the 81 provinces of Turkey contains the information first-hand and second-hand home sales. Migration movements in cities, economic movements throughout the country and some changes in cities (such as opening factories) are some of the factors that affect home sales data.
Some packages need to be used to analyze the data. First of all, these packages were included and the data was taken from csv file.  In order to observe the content of our group data, the head and the tale part were printed.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(dplyr)
library(cluster)
library(factoextra)
evds = read.csv("C:/Users/z00435xw/Desktop/48A Group/housing_data_EVDS.csv")
head(evds[,c(1:5)])
tail(evds[,c(1:5)])
evds[c(90:100),c(1:5)]
```

After the 92nd row, rows gives information about the numerical . Therefore, numerical data was separated from these information rows and put into another data set.

```{r echo=TRUE}
datainfo = evds[c(92:1080),]
evds = evds[c(1:91),]
head(evds[,c(1:5)])
tail(evds[,c(1:5)])

```

The home sales data included data with zeros after the comma. To avoid these problems, zeros are cleared from the data after the comma.

```{r pressure, echo=TRUE}
for(i in c(1:165)){
  evds[,i] <- gsub(",","",evds[,i])
}

evds[, c(2:165)] <- sapply(evds[, c(2:165)], as.numeric)

names(evds)[1] = "Date"

```

In order to convert the Date column to a date format, it was necessary to add days to the Date. That's why the day was added to the Date column.

```{r echo=TRUE}
evds$Date = paste(evds$Date,"01",sep="-")

evds = evds %>%
  mutate(Date=as.Date(Date, format="%Y-%m-%d")) %>%
  mutate(Year=year(Date), Month=month(Date))

head(evds, 10)

```

In the data analysis process, a season column may be required to examine the relationship between sales data and seasons, so the season column was created.

```{r}
find_season <- function(mon){
  season = NULL
  
  if(between(mon, 3, 5)){
    season = "Spring"
  } else if(between(mon, 6, 8)){
    season = "Summer"
  } else if(between(mon, 9, 11)){
    season = "Fall"
  } else{
    season = "Winter"
  }
  
  return(season)
}

evds$Season = sapply(evds$Month, find_season)

head(evds, 10)

head(names(evds),50)

```

As mentioned earlier, the data includes the sales numbers of second-hand and first-hand homes. Here it looked very complicated when naming data. To avoid this situation, the letter "F" was used for naming the first hand data and the letter "S" for the second hand.

```{r}
for(i in c(2:165)){
  name = names(evds)[i]
  splitted = unlist(strsplit(name, "\\."))
  if(splitted[2] == "AKONUTSAT3"){
    names(evds)[i] = paste("F",splitted[3],sep=".")
  } else if(splitted[2] == "AKONUTSAT4"){
    names(evds)[i] = paste("S",splitted[3],sep=".")
  }
}
names(evds)
```

When the data is checked carefully, there is some missing data. To guess what these missing data are:
Total data was analyzed by collecting all data.
As it is realized that it is equal, empty data (NA) are accepted as 0.

```{r echo=TRUE}
evds[,c(2)] - rowSums(evds[,c(3:83)], na.rm = FALSE)
evds[,c(2)] - rowSums(evds[,c(3:83)], na.rm = TRUE)
evds[is.na(evds)] <- 0

```
>Analyzing the Data

A plot line has been drawn to observe the sales movement of the first and second hand houses by years. As can be seen from the graphic, the amount of house sales increased every year.

```{r echo=TRUE}
ggplot(evds, aes(x=Date)) + 
  geom_line(aes(y=S.TOPLAM, color="S")) + 
  geom_line(aes(y=F.TOPLAM, color="F")) +
  theme_minimal() + 
  ggtitle("Total Number of Sales") + 
  labs(x = "Year", y = "Number of Sales")

```
Turkey the behavior of sales in general, the city has been interpreted by comparing the behavior of a relationship between them. As can be seen in the graph, the sales behavior of Adana is similar to the sales data across the country. We cannot generalize for every city, but we can say that the same criteria are effective across the country.

```{r}
ggplot(evds, aes(x=Date, color = Month)) + 
  geom_line(aes(y=S.T1, color="S1")) + 
  geom_line(aes(y=F.T1, color="F1")) +
  theme_minimal() + 
  ggtitle("Adana") + 
  labs(x = "Year", y = "Sales_Count")
```

The most advanced and largest city in Turkey: Ankara and Istanbul. Therefore, the sales data of these two cities were examined separately. When the data of the two cities are analyzed on the graph, the sales data of Istanbul is higher than Ankara. When the sum of the data of all cities is plotted, the total data of Ankara and Istanbul is very high compared to other cities.

```{r}
ggplot(evds, aes(x=Date, color = Month)) + 
  geom_line(aes(y=S.T7, color="S_Ankara")) + 
  geom_line(aes(y=F.T7, color="F_Ankara")) +
  geom_line(aes(y=S.T40, color="S_Istanbul")) + 
  geom_line(aes(y=F.T40, color="F_Istanbul")) +
  theme_minimal() + 
  ggtitle("Istanbul Vs Ankara") + 
  labs(x = "Year", y = "Sales_Count")

plot(colSums(evds[,c(3:83)]),xlab = "City",ylab = "Sutun toplami")
```

####Clustering

By classifying the sales data of the cities according to the similarities of the movement, it is desired to analyze the sales behavior more logically. Therefore, all columns are scaled.

```{r}
evds.scaled=scale(evds[,c(2:165)])
head(evds.scaled)

fit <- kmeans(t(evds.scaled), 5) 
mydata <- data.frame(t(evds.scaled), fit$cluster)

for(i in 1:5){
  print(row.names(mydata[(mydata$fit.cluster==i),]))
  print("")
}
```

First hand only city columns are scaled so that they are grouped by movement similarities.

```{r}
evdsF.scaled=scale(evds[,c(3:83)])
head(evdsF.scaled)

fit <- kmeans(t(evdsF.scaled), 15) 
mydata <- data.frame(t(evdsF.scaled), fit$cluster)

for(i in 1:15){
  print(row.names(mydata[(mydata$fit.cluster==i),]))
  print("")
}
```
Only Second hand city columns are scaled so that they are grouped according to their motion similarity.

```{r echo=TRUE}
evdsS.scaled=scale(evds[,c(85:165)])
head(evdsS.scaled)

fit <- kmeans(t(evdsS.scaled), 5) 
mydata <- data.frame(t(evdsS.scaled), fit$cluster)

for(i in 1:5){
  print(row.names(mydata[(mydata$fit.cluster==i),]))
  print("")
}

```
First hand only city columns used, not scaled so often grouped by size of numbers

```{r echo=TRUE}
evdsF=evds[,c(3:83)]
head(evdsF)

fit <- kmeans(t(evdsF), 5) 
mydata <- data.frame(t(evdsF), fit$cluster)

for(i in 1:5){
  print(row.names(mydata[(mydata$fit.cluster==i),]))
  print("")
}

```

evds2 contains what percentage of the values make up the total, maybe abnormal changes may be caught / a result may be reached:

```{r}
evds2 = evds
evds2[,c(2:83)] = evds2[,c(2:83)]*100/evds2[,2]
evds2[,c(84:165)] = evds2[,c(84:165)]*100/evds2[,84]

```



```{r}
ggplot(evds2, aes(x=Date)) + 
  geom_line(aes(y=S.TOPLAM, color="S")) + 
  geom_line(aes(y=F.TOPLAM, color="F")) +
  theme_minimal() + 
  ggtitle("First and Second Hand Home Sales") + 
  labs(x = "year", y = "")

```



In order to examine the house sales data of the Aegean ve Akdeniz region, whose population has increased considerably during the summer season, some of the cities in the Aegean and Akdeniz Region were selected from all data.
(Antalya, Balıkesir, İzmir, Aydın, )
```{r}

ege_bolge <- evds[,c(1,10,14,43,13,61,166,167,168)]
head(ege_bolge)
```


Between 2013-2020, a bar plot was drawn for Antalya's sales data by months. By observing the year-by-year sales movement, it can be said that the sales have increased each year, and the sales are also increasing every year in the summer months.

```{r}

ege_bolge %>%  group_by(Month,Season) %>% summarise(Sum = sum(F.T12)) %>%
  ggplot(data = ., aes(x = Month, y = Sum, fill = Season)) +
  geom_bar(stat="identity", position = position_dodge(), colour = "blue") +
  theme_minimal() +
  theme(legend.position="top")+
  labs(title = "Antalya")+
  geom_text(aes(label=Sum), vjust=1.6, color="black",
      position = position_dodge(0.9), size=3.5)
```

Between 2013-2020, a line plot was drawn for Balıkesir's sales data by months. By observing the month-by-month sales movement, it can be said that the sales have increased end of the year, an
```{r}

ggplot(ege_bolge, aes(x=Month, y = ege_bolge[,c(2:2)], group = Year, colour = Season)) + 
  geom_line() +
  theme_minimal() +
  theme(legend.position="top")+
  labs(title = "Balikesir")
```

First and second hand sales data between Ankara and Istanbul by years.
```{r}

ggplot(evds, aes(x=Date, color = Month)) + 
  geom_line(aes(y=S.T7, color="S_Ankara")) + 
  geom_line(aes(y=F.T7, color="F_Ankara")) +
  geom_line(aes(y=S.T41, color="S_Istanbul")) + 
  geom_line(aes(y=F.T41, color="F_Istanbul")) +
  theme_minimal() + 
  ggtitle("Comparison") + 
  labs(x = "Year", y = "Sales Count")
```
Total sales dats by years and seasons by selected cities in the aegean region with bar chart

```{r}
#
ege_bolge %>% group_by(Year,Season) %>% summarise(SumData=sum(F.T8, F.T12, F.T41, F.T11, F.T59)) %>% 
    ggplot(data = ., aes(x = Year, y = SumData, fill = Season)) +
      geom_bar(stat="identity", position = position_dodge(), colour = "black") +
      theme_minimal() +
      theme(legend.position="top")+
      labs(title = "Ege_Bolge")+
      geom_text(aes(label=SumData), vjust=1.6, color="black",
        position = position_dodge(0.9), size=3.5)

```


