---
title: "AirBnB Dataset - Exploratory Data Analysis"
author: "his'R'ustu"
date: "8/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

See the description taken from Kaggle page.

### Context
Since 2008, guests and hosts have used Airbnb to expand on traveling possibilities and present more unique, personalized way of experiencing the world. This dataset describes the listing activity and metrics in NYC, NY for 2019.

### Content
This data file includes all needed information to find out more about hosts, geographical availability, necessary metrics to make predictions and draw conclusions.

### Acknowledgements
This public dataset is part of Airbnb, and the original source can be found on this [website](http://insideairbnb.com/).

### Libraries and Dataset
```{r libraries, message=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
library(data.table)

data <- readRDS("data/AB_NYC_2019.rds")
```

## Summary of The Dataset
There are nearly 49K rows and 16 columns. Data types seem correct expect last_review column. It's necessary to convert last_review to date format.

```{r summary}
glimpse(data)
data$last_review <- as.Date(parse_date_time(data$last_review, c('ymd')))
```

There are null values in 2 columns: number_of_reviews and last_review. These are correlated, if there is no reviews than these two value is null in that row and it seems logical.

```{r null}
na_count <-sapply(data, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```

Let's select important columns and see some of the rows as sample.

```{r select}
selected <- select(data, neighbourhood_group, neighbourhood, room_type, price, minimum_nights, number_of_reviews, last_review, reviews_per_month, calculated_host_listings_count, availability_365)
head(selected)
```

There are 3 different room types. One can book a private room or share the room and also one can book an entire place.

```{r values}
print(c(c(unique(selected["neighbourhood_group"])),c(unique(selected["room_type"]))))
```

## Initial Analysis

Let's see the room type distribution (frequency/density).

```{r i-frequency}
ggplot(selected, aes(x=room_type)) +
  geom_bar(stat = "count") +
  labs(x = "room_type")
```

From the distribution graph,

  nearly 52% prefer booking the entire place posted,

  nearly 52% prefer booking a private room,

  the rest 2% prefer booking a shared room.
  

```{r i-density}
ggplot(selected, aes(x=room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  labs(x = "room_type")

```

Moreover, to see the areas with the highest preference in New York, neighborhood group distribution must be analyzed.

```{r n-density}
ggplot(selected, aes(x=neighbourhood_group)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  labs(x = "neighbourhood_group")
```

From the graph, Brooklyn and Manhattan are the leading areas in Airnbnb rental. Followed by Queens, Bronx, and Staten Island. There are a few reasons why for the nature of this distribution. Firstly, Bronx is a relatively dangerous area compared to the other areas. Statistics show that Bronx has the highes crime rate in the city, followed by Queens. In the case of Staten Island, the high-end problem arise along with transportation. Staten Island is known for its over the top luxury rentals. In fact, the area ranks among the most expensive rental estates in the U.S. Moreover, Staten Island is far from the tourist attractions, making it a undesirable location for tourists. Manhattan and Brooklyn lead the touristic facade of the city. Manhattan owns the most frequently visited touristic attractions, thus, it's easier for tourists to commute if they rent an airbnb rental in Manhattan. The same situation rises with Brooklyn, as it offers an extensive night life, restaurants, concept cafes, and fewer tourist attractions. The price of rentals will be analyzed next.

```{r price-hist}
ggplot(selected, aes(x=price)) + 
  geom_histogram(color="black", fill="white", binwidth=70)
```

To check the price range and how many rentals were rented for a specific price, the price distribution should be visualized. Firstly, the statistics for the column, price, are calculated.

```{r price-desc}
c(min(data$price), max(data$price), mean(data$price), median(data$price))
```

From the calculation, it's clearly seen that even though price has a large range, the median and the mean of the price are relatively low. To see the frequency of each price, ggplot is used to visualize. The limit for the x axis, price, is selected as 1000. By doing so, the plot becomes easily readable and outliers are removed. From the graph, the price frequency lies on the left-hand side. The Airbnb users primarily prefer cheaper rentals as the majority of the price frequency is shifted to the left side of the graph.

```{r price-hist-lim, warning=FALSE}
ggplot(selected, aes(x=price)) + 
  geom_histogram(color="black", fill="white", binwidth=20) +
  xlim(c(0,1000))
```



```{r price-room-types}
aggregate(selected$price, list(selected$room_type), mean)
```

The code below provides the neighborhoods mostly prefered by Airbnb users.

```{r top10-neighbour}
tail(names(sort(table(selected$neighbourhood))), 10)

z <- tail(names(sort(table(selected$neighbourhood))), 10)
ggplot(selected[selected$neighbourhood %in% z,], aes(x=neighbourhood)) +
  geom_bar(stat = "count") +
  labs(x = "neighbourhood") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Moreover, the code below shows the average price for each type of rental. From the results, Entire home or apartments have the highest price mean as expected, followed by private rooms and shared rooms, again, as expected.

```{r price-neighbours}
aggregate(selected$price, list(selected$room_type), mean)
```

The plot below shows the prices based on the location of the listing. From the plot, It's observed that Manhattan has the most number of listings and the highest price rentals. Followed by Brooklyn. Bronx, Queen, and Staten Island have the lowest price listings and the lowest number of listings. Due to the reasons mentioned before.

```{r loc-price-availability, message=FALSE}
ggplot(data, aes(x=neighbourhood_group, y=price)) + 
  geom_point(aes(col=room_type, size=availability_365)) + 
  ylim(c(0, 10000)) + 
  labs(title="Location Vs Price", 
       subtitle="(availability, listing space types)", 
       x="Location", 
       y="Price", 
       caption = "Source: AirBnB")
```